Analysis of the 2005--2015 Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2016-08-19 results.tex
improved new figure 8

% \begin{figure*}[t]
% 	\centering
% 	\includegraphics[scale=0.6]{figures/pdf/Figure09.pdf} 
% 	\caption{ Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}. The lines represent the linear regression fit of data. The correlation coefficients (R) are represented for different combination of data.}
% 	\label{fig:regression}
% \end{figure*}

>>>>

\begin{figure}[h]%[t]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-08} 
	\caption{Relationship between $k-M$ slope and $b-value$ of three Iranian tectonic seismic zones (this study) and three other studies of Mexican zones \citep{Telesca2013}, Pannonia zones \citep{Telesca2014}, and synthetic data \citep{Telesca2014-pone}. The lines represent the linear regression fit of data. The correlation coefficients (R) are represented for different combination of data.}
	\label{fig:regression}
\end{figure}
